\textbf{Measuring Depression and Anxiety with 4 items? Adaptation of the PHQ-4 to increase its Sensitivity to Subclinical Variability}

### 2025-06-06 paper/5_Collabra/manuscript.tex
done

\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

@@

\abstract{The PHQ-4 is an ultra-brief (4 items) screening questionnaire
for depression and anxiety. In this brief report, we test the benefits
of adding one additional response option (``Once or twice'', in between
``Not at all'' and ``Several days'') to improve the scale's sensitivity
to milder alterations, and thus increase its usefulness in subclinical
populations. In study 1 (N=485), we provide evidence using Item Response
Theory (IRT) that the new response option does improve the scale's
psychometric quality and extends the sensitivity to the measured
constructs on the lower end of the spectrum. In study 2 (N=836), we show
that the refined version offers an improved sensitivity to subclinical
variability in depression (indexed by the BDI-II) as compared to the
original version. In conclusion, adding the ``once or twice'' response
option is a low-cost no-downsides way of increasing the PHQ-4's
sensitivity to subclinical variability, making it a tool of choice for
general population research.}

@@

\authornote{\par{\addORCIDlink{Dominique
Makowski}{0000-0001-5375-9967}}\par{\addORCIDlink{An Shu
Te}{0000-0002-9312-5552}}\par{\addORCIDlink{Ana
Neves}{0009-0006-0020-7599}}\par{\addORCIDlink{S.H. Annabel
Chen}{0000-0002-1540-5516}} 
\par{ }
\par{     \begin{tcolorbox}[enhanced jigsaw, breakable, rightrule=.15mm, leftrule=.75mm, toprule=.15mm, colframe=quarto-callout-note-color-frame, left=2mm, opacityback=0, colback=white, arc=.35mm, bottomrule=.15mm]

This preprint is a non-peer-reviewed work from the
\href{https://realitybending.github.io/}{\textbf{Reality Bending Lab}}.
\begin{center}
\includegraphics[width=0.2\textwidth,height=\textheight]{manuscript_files/mediabag/ReBeL_LogoOnly_hu114.png}
\end{center}

@@

While the scale has been validated and used in the general population
and non-clinical samples (\citeproc{ref-hajek2020prevalence}{Hajek \&
König, 2020}; \citeproc{ref-lowe20104}{Löwe et al., 2010}), its initial
purpose was to reliably discriminate and identify potential MDD/GAD
patients. This discriminative goal materializes in the scale's design
and the existence of categorical cut-offs, which does not necessary
entail a focus on the sensitivity to milder mood alterations. In
particular, the gap between the two lowest possible answers, ``Not at
all'' and ``Several days'', is quite large and possibly leaves out the
possibility of more subtle occurrences. While this is not necessarily an
issue in clinical and diagnostic contexts, it might lead to a
sub-optimal discrimination of affective levels on the lower end of the
spectrum, important for instance in the context of subclinical
variability quantification.

This brief report aims at testing the possibility of enhancing - with
minimal changes to the original scale - the PHQ-4 sensitivity to mild
mood level inflections. In the first study, we will evaluate whether the
new response option is prevalently used by participants, and whether it
does capture a specific part of the latent measure. In the second study,
we will compare the refined PHQ-4 version to the original one in terms
of sensitivity to subclinical variability in depression, using the Beck
Depression Inventory (BDI-II, \citeproc{ref-beck1996beck}{Beck et al.,
1996}) and the State Trait Anxiety Inventory (STAI-5,
\citeproc{ref-zsido2020development}{Zsido et al., 2020}) as our
ground-truth measures of depression and anxiety.

@@

For the refined version, we added a ``Once or twice'' option between
``Not at all'' and ``Several days''in order to better capture potential
mild mood inflections (see \citeproc{ref-dobson1979equidistant}{Dobson
\& Mothersill, 1979} for the choice of the label). This new option was
scored as 0.5 to preserve the same scoring as the original version.

@@

\includegraphics[width=1\textwidth,height=\textheight]{../../study1/figures/figure1.png}

@@

The reliability of the anxiety (\(Cronbach's~\alpha = 0.903\); RMSEA =
0.031) and depression (\(Cronbach's~\alpha = 0.841\); RMSEA = 0.044)
subscales is excellent. The proportion of response types stratified by
item (see Figure~\ref{fig-one}) shows that the new ``Once or twice''
option was the most prevalent response for all items (on average
selected in 29.12\% of cases).

@@

Item Response Theory (IRT) provides insights into how well items and
responses capture an underlying latent trait \(\theta\). For each of the
subscales, we fitted a unidimensional graded response model (GRM,
\citeproc{ref-samejima1997graded}{Samejima, 1997}). For anxiety, the two
items captured 89.2\% of the variance of the latent anxiety dimension
(\(\theta_{anxiety}\)). The discrimination parameters suggested that the
first item was less precise (\(\alpha = 3.42\)) than the second item
(\(\alpha = 12.55\)) in its ability to discriminate between various
levels of anxiety (i.e., each response on the second item covers a more
exclusive range of \(\theta_{anxiety}\), as can be seen in
Figure~\ref{fig-one}). The two depression items captured 82.8\% of the
variance of its latent trait (\(\theta_{depression}\)), and the opposite
pattern was found: the first item had a higher precision
(\(\alpha = 16.46\)) than the first (\(\alpha = 2.41\)). However, it is
important to note that the ``less precise'' items were also the ones
covering a larger portion of the latent space (being more sensitive
especially on the lower end of the spectrum), offering an interesting
trade-off between sensitivity and precision. Importantly for our
objective, the added ``Once or twice'' option did cover a selective and
unique portion of the latent space.

@@

One natural methodological limitation pertains to the interpretation of
the latent dimensions in an IRT framework applied to pairs of items. In
this study's context, references to for instance ``the latent anxiety
dimension'' merely corresponds to the amalgamation of the two items of
the anxiety subscale, and not to a more general and valid true anxiety
factor.

@@

The initial sample consisted of 1053 participants, recruited (181 were
recruited on \emph{Prolific}, 772 students from the University of Sussex
via \emph{SONA}, and the rest through convenience sampling as part of
dissertation students' data collection). We used attention checks as the
primary target for participant exclusion. We excluded 194 participants
(18.42\%) for failing at least one attention check, and 23 (2.18\%) that
were outliers (\(|z_{robust}| > 2.58\)) on measures significantly
related to the probability of failing attention checks (namely, the
standard deviation of all the items of the IAS, as well as the the
multivariate distance obtained with the OPTICS algorithm, see
\citeproc{ref-theriault2024check}{Thériault et al., 2024}). The
experiment duration was not related to the probability of failing
attention checks and was thus not used as an exclusion criterion.

@@

In this sample, 51 participants (6.10\%) were labelled as having
Depression, as indexed by the self-reported presence of MDD together
with the use of a treatment (antidepressent, anxiolytic and/or therapy),
and 87 participants (10.41\%) were labelled as having Anxiety, as
indexed by the self-reported presence of GAD or Panic Disorder, also
together with the use of a treatment.

@@

Participants were randomly assigned to complete either the original or
refined version of the PHQ-4, which included one additional response
option (``Once or twice'') scored 0.5 (creating more possible total
scores - 0.5, 1.5, 2.5, etc.).

@@

The short version of the State-Trait Anxiety Inventory (STAI-5,
\citeproc{ref-zsido2020development}{Zsido et al., 2020}) was used as a
ground truth measure of anxiety. This abridged version of the STAI
(\citeproc{ref-spielberger1970manual}{Spielberger, 1970}) includes 5
items rated on a 4-point Likert scale. Changes were made in the
instructions from asking \emph{``how participants feel right now''} to
\emph{``over the past 2 weeks''} to keep it consistent with the
instructions of the PHQ-4 and BDI-II. A general score of anxiety was
computed by averaging all the items.

Participants were also asked to complete two questionnaires of
interoception, namely the Interoceptive Accuracy Scale (IAS - 21 items
rated on analog scales, \citeproc{ref-murphy2020testing}{Murphy et al.,
2020}) and the Multidimensional Assessment of Interoceptive Awareness
(MAIA-2 - 37 items, \citeproc{ref-mehling2018multidimensional}{Mehling
et al., 2018}).

@@

The original or refined version of the PHQ-4 was followed by the BDI-II,
STAI-5, IAS, and MAIA-2, presented in random order. The IAS and the
MAIA-2 were included as part of another study focused on interoception,
and were only used in this stud as part of data quality control checks.

@@

\includegraphics[width=1\textwidth,height=\textheight]{../../study2/analysis/2_analysis_files/figure-html/figure-1.png}

@@

The linear regression predicting the BDI-II total score with the PHQ-4
depression score showed no interaction related to the PHQ-4 version
(\(\Delta Intercept_{\text{refined}} =  -0.13,~95\%~CI~[-1.73, 1.47],~t(832) =  -0.16,~p = 0.871\);
\(\Delta \beta_{\text{refined}} = -0.05,~95\%~CI~[-0.70, 0.60],~t(832) = -0.15,~p = 0.883\)),
suggesting no differences in the relationship pattern between the two
versions (see Figure~\ref{fig-two}).

@@

Finally, although we used a stricter criterion for classifying
participants as having a depression or an anxiety disorder by
restricting it to participants also reporting undergoing a medical
treatment, it was still based on self-reported data. Studies in
controlled clinical settings are needed to confirm the potential
benefits of the refined PHQ-4 in mood disorders detection accuracy.

@@

The objective of this study was to test the introduction of a ``Once or
twice'' response option to the PHQ-4 to enhance its sensitivity to
milder mood fluctuations. In the first study, we showed that the new
response option was used prevalently by participants and did capture a
unique portion of the depression and anxiety underlying dimensions. In
the second study, we showed that the refined version of the PHQ-4 was
able to better differentiate lower levels of depression compared to the
original version, while remaining comparable. Although the benefits of
this refinement appear to be fairly minor, and particularly marked for
the depression score compared to anxiety, this cost-free improvement
appear useful to implement when measuring depression and anxiety using
the PHQ-4 ultra-short screening questionnaire.

@@

@@

@@

@@

>>>>

\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother

@@

\abstract{The PHQ-4 is an ultra-brief (4 items) screening questionnaire
for depression and anxiety. In this brief report, we test the benefits
of adding one additional response option (``Once or twice'', in between
``Not at all'' and ``Several days'') to improve the scale's sensitivity
to milder alterations, and thus increase its usefulness in subclinical
populations. In study 1 (N=485), we provide evidence using Item Response
Theory (IRT) that the new response option does improve the scale's
psychometric quality and extends the sensitivity to the measured
constructs on the lower end of the spectrum. In study 2 (N=836), we show
that the refined version offers an improved sensitivity to subclinical
variability in depression (indexed by the BDI-II) as compared to the
original version. In conclusion, adding the ``once or twice'' response
option is a low-cost way of increasing the PHQ-4's sensitivity to
subclinical variability, making it a tool of choice for general
population research.}

@@

\authornote{\par{\addORCIDlink{Dominique
Makowski}{0000-0001-5375-9967}}\par{\addORCIDlink{An Shu
Te}{0000-0002-9312-5552}}\par{\addORCIDlink{Ana
Neves}{0009-0006-0020-7599}}\par{\addORCIDlink{S.H. Annabel
Chen}{0000-0002-1540-5516}} 
\par{ }
\par{     \begin{tcolorbox}[enhanced jigsaw, colback=white, toprule=.15mm, opacityback=0, arc=.35mm, breakable, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, rightrule=.15mm, left=2mm, leftrule=.75mm]

This preprint is a non-peer-reviewed work from the
\href{https://realitybending.github.io/}{\textbf{Reality Bending Lab}}.
\begin{center}
\includegraphics[width=0.2\linewidth,height=\textheight,keepaspectratio]{manuscript_files/mediabag/ReBeL_LogoOnly_hu114.png}
\end{center}

@@

While the scale has been validated and used in the general population
and non-clinical samples (\citeproc{ref-hajek2020prevalence}{Hajek \&
König, 2020}; \citeproc{ref-lowe20104}{Löwe et al., 2010}), its initial
purpose was to reliably discriminate and identify potential MDD/GAD
patients. This discriminative goal materializes in the scale's design
and the existence of categorical cut-offs, which does not necessarily
entail a focus on the sensitivity to milder mood alterations. In
particular, the gap between the two lowest possible answers, ``Not at
all'' and ``Several days'', is quite large and possibly leaves out the
possibility of more subtle occurrences. While this is not necessarily an
issue in clinical and diagnostic contexts, it might lead to a
sub-optimal discrimination of affective levels on the lower end of the
spectrum, important for instance in the context of subclinical
variability quantification.

\textbf{Enabling a more precise assessment of low-severity alterations
is important, as milder symptoms are significant predictors of future
clinical disorders and are associated with present functional
impairments and reduced quality of life
(\citeproc{ref-cuijpers2004subthreshold}{Cuijpers \& Smit, 2004};
\citeproc{ref-judd1998major}{Judd et al., 1998}). In addition, the
growing reliance on large-scale, often online, psychological and
epidemiological surveys, to monitor population-level mental health,
evaluate interventions, or track responses to global stressors such as
pandemics or geopolitical crises, demands tools that are both brief and
sensitive to small but meaningful fluctuations.}

This brief report aims at testing the possibility of enhancing - with
minimal changes to the original scale - the PHQ-4 sensitivity to mild
mood level inflections. In the first study, we will evaluate whether the
new response option is prevalently used by participants, and whether it
does capture a specific part of the construct. In the second study, we
will compare the refined PHQ-4 version to the original one in terms of
sensitivity to subclinical variability in depression, using the Beck
Depression Inventory (BDI-II, \citeproc{ref-beck1996beck}{Beck et al.,
1996}) and the Trait scale of the State-Trait Anxiety Inventory (STAI-5,
\citeproc{ref-zsido2020development}{Zsido et al., 2020}) as our
ground-truth measures of depression and anxiety.

@@

For the refined version, we added a ``Once or twice'' option between
``Not at all'' and ``Several days''in order to better capture potential
mild mood inflections (see \citeproc{ref-dobson1979equidistant}{Dobson
\& Mothersill, 1979} for the choice of the label).

@@

\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{../../study1/figures/figure1.png}

@@

The consistency of the anxiety (\(Cronbach's~\alpha = 0.903\)) and
depression (\(Cronbach's~\alpha = 0.841\)) subscales is excellent
(responses were treated as ordinal). The proportion of response types
stratified by item (see Figure~\ref{fig-one}) shows that the new ``Once
or twice'' option was the most prevalent response for all items (on
average selected in 29.12\% of cases).

@@

Item Response Theory (IRT) provides insights into how well items and
responses capture an underlying latent trait \(\theta\). For each of the
subscales, we fitted a unidimensional graded response model (GRM,
\citeproc{ref-samejima1997graded}{Samejima, 1997}). For anxiety, the
latent anxiety dimension (\(\theta_{anxiety}\)) captured 89.2\% of the
total variance across the two items (RMSEA = 0.031). The discrimination
parameters suggested that the first item was less precise
(\(\alpha = 3.42\)) than the second item (\(\alpha = 12.55\)) in its
ability to discriminate between various levels of anxiety (i.e., each
response on the second item covers a more exclusive range of
\(\theta_{anxiety}\), as can be seen in Figure~\ref{fig-one}). The
latent depression trait (\(\theta_{depression}\)) The two depression
items captured 82.8\% of the total variance across the two items (RMSEA
= 0.044), and the opposite pattern was found: the first item had a
higher precision (\(\alpha = 16.46\)) than the second
(\(\alpha = 2.41\)). However, it is important to note that the ``less
precise'' items were also the ones covering a larger portion of the
latent space (being more sensitive especially on the lower end of the
spectrum), offering an interesting trade-off between sensitivity and
precision. Most importantly for our objective, the added ``Once or
twice'' option did cover a selective and unique portion of the latent
space.

@@

\textbf{One natural methodological limitation pertains to the
application of the IRT framework to pairs of items. While this is
statistically sound (the graded model utilizes the full response pattern
information and does not solely rely on the item covariance matrix for
parameter estimation), it is important to underline that in our study's
context, ``the latent anxiety/depression dimension'' merely corresponds
to the amalgamation of the two items of the anxiety or depression
subscale, and not to a more general and independent latent anxiety or
depression factor.}

\textbf{In summary, the main take-away of this first study is that the
``Once or twice'' response option appears as a popular choice, which
begs the question of its usefulness in capturing more fine-grained
variations of the underlying dimensions as measured by independent
tools.}

@@

The initial sample consisted of 1053 participants, recruited (181 were
recruited on \emph{Prolific}, 772 students from the University of Sussex
via \emph{SONA}, and the rest through convenience sampling as part of
dissertation students' data collection). We used attention checks as the
primary target for participant exclusion. We excluded 194 participants
(18.42\%) for failing at least one attention check, and 23 (2.18\%) that
were outliers (\(|z_{robust}| > 2.58\)) on measures significantly
related to the probability of failing attention checks (namely, the
standard deviation of all the items of the Interoceptive Accuracy Scale,
as well as the the multivariate distance obtained with the OPTICS
algorithm, see \citeproc{ref-theriault2024check}{Thériault et al.,
2024}). The experiment duration was not related to the probability of
failing attention checks and was thus not used as an exclusion
criterion.

@@

In this sample, 51 participants (6.10\%) were coded as having
Depression, as indexed by the self-reported presence of MDD together
with the use of a treatment (antidepressent, anxiolytic and/or therapy),
and 87 participants (10.41\%) were coded as having Anxiety, as indexed
by the self-reported presence of GAD or Panic Disorder, also together
with the use of a treatment.

@@

Participants were randomly assigned to complete either the original or
refined version of the PHQ-4, which included one additional response
option (``Once or twice''). \textbf{To preserve comparability with the
original PHQ-4 scoring system and avoid altering the scale's total score
range or established cut-off thresholds, we assigned the new response
option a value of 0.5, placing it midway between ``Not at all'' (0) and
``Several days'' (1). While this scoring assumes equal spacing between
response options - a common but imperfect convention in ordinal scales -
it offers a pragmatic compromise between conceptual fidelity and applied
utility.}

@@

The short version of the trait subscale of the State-Trait Anxiety
Inventory (STAI-5, \citeproc{ref-zsido2020development}{Zsido et al.,
2020}) was used as a ground truth measure of anxiety. This abridged
version of the STAI (\citeproc{ref-spielberger1970manual}{Spielberger,
1970}) includes 5 items rated on a 4-point Likert scale. Changes were
made in the instructions from asking \emph{``how participants feel right
now''} to \emph{``over the past 2 weeks''} to keep it consistent with
the instructions of the PHQ-4 and BDI-II. A general score of anxiety was
computed by averaging all the items.

Participants were also asked to complete two questionnaires of
interoception, namely the Interoceptive Accuracy Scale (IAS, 21 items
rated on analog scales, \citeproc{ref-murphy2020testing}{Murphy et al.,
2020}) and the Multidimensional Assessment of Interoceptive Awareness
(MAIA-2 - 37 items, \citeproc{ref-mehling2018multidimensional}{Mehling
et al., 2018}).

@@

The original or refined version of the PHQ-4 was followed by the BDI-II,
STAI-5, IAS, and MAIA-2, presented in random order. The IAS
(\citeproc{ref-murphy2020testing}{Murphy et al., 2020}) and the MAIA-2
(\citeproc{ref-mehling2018multidimensional}{Mehling et al., 2018}) were
included as part of another focused on interoception, and were only used
in this study as part of data quality control checks.

@@

\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{../../study2/analysis/2_analysis_files/figure-html/figure-1.png}

@@

\textbf{A linear model testing the interaction effect \(\Delta\) of the
refined condition on the intercept (representing by how much the value
of the outcome when the PHQ score is 0 changes for the refined version
compared the original) and slope (its increase or decrease by the
refined version compared to the original) of the relationship between
the PHQ-4 depression score and the BDI-II total score was fitted.} The
model predicting the BDI-II total score with the PHQ-4 depression score
showed no interaction related to the PHQ-4 version
(\(\Delta Intercept_{\text{refined}} =  -0.13,~95\%~CI~[-1.73, 1.47],~t(832) =  -0.16,~p = 0.871\);
\(\Delta \beta_{\text{refined}} = -0.05,~95\%~CI~[-0.70, 0.60],~t(832) = -0.15,~p = 0.883\)),
suggesting no differences in the relationship pattern between the two
versions (see Figure~\ref{fig-two}).

@@

\textbf{One of the potential limitation of our study includes the choice
of the measures used as external ``ground-truth'' of depression and
anxiety, namely the BDI-II and the STAI-5. For instance, there is
ongoing debate about the STAI's discriminant validity (which might
extend to its short form used in the present study). A recent
meta-analysis reported that trait anxiety scores were more strongly
associated with depressive than anxiety disorders
(\citeproc{ref-knowles2020specificity}{Knowles \& Olatunji, 2020}),
suggesting that the scale may rather capture general negative affect
than specifically anxiety. Regarding the BDI-II, existing evidence that
suggests its relative lack of sensitivity for low-severity depression
(\citeproc{ref-olino2012measuring}{Olino et al., 2012}) - comparable to
similar instruments of its size (e.g., CES-D), and an improvement over
the BDI-I (\citeproc{ref-wahl2014standardization}{Wahl et al., 2014}) -
put into question its choice for our goal of showing increased
sub-clinical sensitivity. Thus, future studies should verify these
findings with alternative measures of anxiety and depression and
clinically assessed populations.}

Indeed, although we used a stricter criterion for classifying
participants as having a depression or an anxiety disorder by
restricting it to participants also reporting undergoing a medical
treatment, it was still based on self-reported data. Studies in
controlled clinical settings are needed to confirm the potential
benefits of the refined PHQ-4 in mood disorders detection accuracy.

@@

The objective of this study was to test the introduction of a ``Once or
twice'' response option to the PHQ-4 to enhance its sensitivity to
milder mood fluctuations. In the first study, we showed that the new
response option was used prevalently by participants and did capture a
unique portion of the depression and anxiety underlying dimensions. In
the second study, we showed that the refined version of the PHQ-4 was
able to better differentiate lower levels of depression compared to the
original version, while remaining comparable. Although the benefits of
this refinement appear to be fairly minor, and particularly marked for
the depression score compared to anxiety, this low-cost improvement
appear useful to implement when measuring depression and anxiety using
the PHQ-4 ultra-short screening questionnaire.

\textbf{While adding granularity to the response format appears useful
for the PHQ-4, it is possible that similar benefits could be found with
other scales and measures. While the use of a limited, highly
discriminating set of response options is understandable for specific
applications (e.g., clinical diagnosis), we recommend future studies to
investigate response format and its potential improvement for other
scales used in online surveys and general population research.}

@@

\bibitem[\citeproctext]{ref-cuijpers2004subthreshold}
Cuijpers, P., \& Smit, F. (2004). Subthreshold depression as a risk
indicator for major depressive disorder: A systematic review of
prospective studies. \emph{Acta Psychiatrica Scandinavica},
\emph{109}(5), 325--331.

@@

\bibitem[\citeproctext]{ref-judd1998major}
Judd, L. L., Akiskal, H. S., Maser, J. D., Zeller, P. J., Endicott, J.,
Coryell, W., Paulus, M. P., Kunovac, J. L., Leon, A. C., Mueller, T. I.,
et al. (1998). Major depressive disorder: A prospective study of
residual subthreshold depressive symptoms as predictor of rapid relapse.
\emph{Journal of Affective Disorders}, \emph{50}(2-3), 97--108.

\bibitem[\citeproctext]{ref-knowles2020specificity}
Knowles, K. A., \& Olatunji, B. O. (2020). Specificity of trait anxiety
in anxiety and depression: Meta-analysis of the state-trait anxiety
inventory. \emph{Clinical Psychology Review}, \emph{82}, 101928.

@@

\bibitem[\citeproctext]{ref-olino2012measuring}
Olino, T. M., Yu, L., Klein, D. N., Rohde, P., Seeley, J. R., Pilkonis,
P. A., \& Lewinsohn, P. M. (2012). Measuring depression using item
response theory: An examination of three measures of depressive
symptomatology. \emph{International Journal of Methods in Psychiatric
Research}, \emph{21}(1), 76--85.

@@

\bibitem[\citeproctext]{ref-wahl2014standardization}
Wahl, I., Löwe, B., Bjorner, J. B., Fischer, F., Langs, G., Voderholzer,
U., Aita, S. A., Bergemann, N., Brähler, E., \& Rose, M. (2014).
Standardization of depression measurement: A common metric was developed
for 11 self-report depression measures. \emph{Journal of Clinical
Epidemiology}, \emph{67}(1), 73--86.
